\ttitle

### 2015-08-25 Chapters/Discussion.tex
Discussion - more updates

%################################################################################
\section{Prehabilitation,improving aerobic capacity and mitigating risk}
%################################################################################
In Chapters \ref{ch_cpet_jaundice} and \ref{ch_bodycomp} we examined the preoperative patient factors that had an adverse effect on aerobic capacity.
A better understanding of the factors that affect $\dot{V}_{O_2}$ may identify potential therapeutic targets or modifiable risk factors that may be used to improve patient fitness and mitigate the risks of surgery.
We found that female sex, high body mass index, anaemia, presence of cancer and elevated CRP were all associated with either a low $\dot{V}_{O_2}$AT or a low $\dot{V}_{O_2}$Peak.

@@

Our results therefore support the emerging view that routine preoperative biliary drainage should no longer be performed in all patients scheduled to undergo a pancreaticoduodenectomy.

@@

@@

Early recognitioon and aggressive management of complications is therefore important in mitigating the harmful long-term effects of such adverse events and the associated inflammation.

%################################################################################
\subsection{Body composition}
%################################################################################
Overweight and obese patients had significantly lower $\dot{V}_{O_2}$AT and $\dot{V}_{O_2}$Peak in spite of no significant increase in known cardiac or respiratory comorbidities. 
We present a detailed analysis of the relationship between body composition and preoperative cardiopulmonary exercise testing in chapter \ref{ch_bodycomp}.
This has not been reported before in surgical patients to the best of out knowledge.

The loss of skeletal muscle mass in patients with pancreatic cancer and spurious correlation with obesity due to correction for total body weight may partly explain the low $\dot{V}_{O_2}$ in these patients. 
Low aerobic capacity as measured by cardiopulmonary exercise testing must be interpreted with caution in overweight/obese patients and in patients with pancreatic cancer. 
This is especially true for $\dot{V}_{O_2}$ that has been scaled for total body weight.
Further studies must evaluate other parameters such as $O_2$Pulse or $\dot{V}_E/\dot{V}_{O_2}$ for their ability to predict postoperative outcomes. 
With the significant increase in the proportion of obese patients undergoing major surgery and the presence of sarcopenic-obesity in patients with pancreatic cancer, poor performance at cardiopulmonary exercise testing may not necessarily be related to cardiac or pulmonary function.

%################################################################################
Moreover, low aerobic capacity was not associated with documented cardiovascular or respiratory comorbidity or with an elevated POSSUM physiology score.
It is possible that most patients with significant cardiac or respiratory comorbidity were identified as unsuitable for surgery and therefore were never subject to cardiopulmonary exercise testing. 
Alternatively, it is possible that these patients did very poorly at cardiopulmonary exercise testing and this, in addition to their cardiorespiratory medical history precluded them from surgery.
We did not include any patients who did not have an operation and this may have introduced a selection bias.
%################################################################################

@@

\subsection{Prehabilitation}

%using cpet to assess impact of neo-adjuvant treatment
%recommend prehab for neoadj in pancreatic cancer
%different types of surgery may need different levels of preparation

%boereboom_forming_2015

>>>>

%################################################################################
\section{Prehabilitation, improving aerobic capacity and mitigating risk}
%################################################################################
In Chapters \ref{ch_cpet_jaundice} and \ref{ch_bodycomp} we examined the preoperative patient factors that had an adverse effect on aerobic capacity.
A better understanding of the factors that affect $\dot{V}_{O_2}$ may identify potential therapeutic targets or modifiable risk factors that may be used to improve patient fitness and mitigate the risks of surgery.
We found that female sex, high body mass index, anaemia, presence of cancer and elevated CRP were all associated with either a low $\dot{V}_{O_2}$AT or a low $\dot{V}_{O_2}$Peak.

@@

Our results support the emerging view that routine preoperative biliary drainage should no longer be performed in all patients scheduled to undergo a pancreaticoduodenectomy.

@@

%################################################################################
\subsection{Body composition}
%################################################################################
Overweight and obese patients had significantly lower $\dot{V}_{O_2}$AT and $\dot{V}_{O_2}$Peak in spite of no significant increase in known cardiac or respiratory comorbidities. 
We present a detailed analysis of the relationship between body composition and preoperative cardiopulmonary exercise testing in chapter \ref{ch_bodycomp}.
This has not been reported before in surgical patients to the best of our knowledge.

The loss of skeletal muscle mass in patients with pancreatic cancer and spurious correlation with obesity due to correction for total body weight may partly explain the low $\dot{V}_{O_2}$ in these patients. 
Low aerobic capacity as measured by cardiopulmonary exercise testing must be interpreted with caution in overweight/obese patients and in patients with pancreatic cancer. 
This is especially true for $\dot{V}_{O_2}$ that has been scaled for total body weight.
Further studies must evaluate other parameters such as $O_2$Pulse or $\dot{V}_E/\dot{V}_{O_2}$ for their ability to predict postoperative outcomes. 
The proportion of obese patients undergoing major surgery is increasing. 
Moreover, sarcopenia and sarcopenic-obesity are recognised as an important adverse prognostic feature in pancreatic cancer \parencite{tan_sarcopenia_2009, peng_impact_2012} and is associated with increased postoperative complications after pancreaticoduodenectomy \parencite{joglekar_sarcopenia_2015, pausch_cachexia_2012}.
Sarcopenia was also an independent risk factor for an elevated postoperative systemic inflammatory response in patients with colorectal cancer \parencite{reisinger_sarcopenia_2015}.

Our results suggest that poor performance at cardiopulmonary exercise testing may not necessarily be related to only cardiac or pulmonary function. 
Body composition appears to not only affect aerobic capacity but also systemic inflammation. 
Improvements in body composition are achievable through nutritional supplementation \parencite{machado_whey_2015} as well as increased physical activity.

%%################################################################################
%Moreover, low aerobic capacity was not associated with documented cardiovascular or respiratory comorbidity or with an elevated POSSUM physiology score.
%It is possible that most patients with significant cardiac or respiratory comorbidity were identified as unsuitable for surgery and therefore were never subject to cardiopulmonary exercise testing. 
%Alternatively, it is possible that these patients did very poorly at cardiopulmonary exercise testing and this, in addition to their cardiorespiratory medical history precluded them from surgery.
%We did not include any patients who did not have an operation and this may have introduced a selection bias.
%%################################################################################

One of the biggest factors in improving both short-term and long-term outcomes after cancer surgery has been the centralisation of cancer cancer and the associated specialisation of surgeons.

Birkmeyer and co-workers reported in 1999 that hospital volume was not only related to postoperative mortality and morbidity but also to long-term cancer survival in patients undergoing pancreaticoduodenectomy.

@@

Early recognition and aggressive management of complications is therefore important in mitigating the harmful long-term effects of such adverse events and the associated inflammation.

@@
